Appendix S1

### 2020-04-22 manuscript/appendix.Rmd
note that lagos-gis cannot be symlinked

# compute per huc tile drainage
# load huc4s
# study_bbox    <- st_read("data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
# hu4_focal     <- st_read("data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
# hu4_focal     <- st_crop(st_transform(hu4_focal, st_crs(study_bbox)), study_bbox)
# http://dx.doi.org/10.5066/F7W37TDP
# library(exactextractr)
# r <- raster("data/SubsurfaceDrainExtentMW_2012.tif")
# test <- st_cast(hu4_focal, "MULTIPOLYGON")
# test$tile_drainage <- exact_extract(r, test, "sum")
# saveRDS(test, "data/tile_drainage.rds")
test <- readRDS("../data/tile_drainage.rds")
test2 <- left_join(test, dt, by = c("ZoneID" = "hu4_zoneid"))

>>>>

test  <- readRDS("../data/tile_drainage.rds")
test2 <- left_join(test, dt, by = c("ZoneID" = "hu4_zoneid"))
